\documentclass[a4paper,10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[
  a4paper,
  top=1.45cm,
  bottom=1.35cm,
  left=1.55cm,
  right=1.55cm
]{geometry}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{array}

\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{transparent}
\usepackage{hyperref}

\definecolor{ink}{HTML}{111827}
\definecolor{muted}{HTML}{4B5563}
\definecolor{soft}{HTML}{F3F4F6}
\definecolor{line}{HTML}{D1D5DB}
\definecolor{linkblue}{HTML}{1D4ED8}
\definecolor{accent}{HTML}{0F172A}

\hypersetup{
  colorlinks=true,
  linkcolor=accent,
  urlcolor=linkblue,
  pdftitle={Dídac Llorens -- Cover Letter -- Assaia Software Engineer},
  pdfauthor={Dídac Llorens},
  pdfsubject={Cover letter for Assaia Software Engineer role},
  pdfkeywords={Software Engineer, ML Core, ML pipelines, Python, backend, tooling, Assaia, Dídac Llorens}
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.78em}
\urlstyle{same}
\color{ink}

\newcommand{\sep}{\textcolor{line}{\quad|\quad}}
\newcommand{\lettersection}[1]{%
  \vspace{0.25em}%
  {\large\bfseries\ttfamily\color{accent}#1}\par
  \vspace{0.25em}%
  {\color{line}\hrule}%
  \vspace{0.85em}%
}

\begin{document}
\small

{\Huge\bfseries\ttfamily Dídac Llorens}\par
\vspace{0.25em}
{\large\ttfamily Software Engineering · ML/AI · Backend / Tooling}\par
\vspace{0.45em}
{\scriptsize\ttfamily
\href{mailto:didacllorensbravo@hotmail.com}{didacllorensbravo@hotmail.com}
\sep
\href{https://didacll.github.io/}{Portfolio}
\sep
\href{https://github.com/DidacLL}{GitHub}
\sep
\href{https://www.linkedin.com/in/didacllorens/}{LinkedIn}
}\par

\vspace{1.4em}
{\color{line}\hrule}
\vspace{1.4em}

\begin{tabularx}{\linewidth}{@{}>{\bfseries\ttfamily\color{muted}}p{2.65cm} X@{}}
To & Assaia hiring team\\
Role & Software Engineer -- ML Core\\
Location & Remote, Spain\\
Date & June 28, 2026 \resizebox{0pt}{!}{\textcolor{white}{Software engineer with a backend and systems-oriented profile, focused on building reliable tooling, APIs and pipeline support around AI/ML local workflows. Best aligned candidate, with clear intention to focus his career growth at this position. Software Engineering specialized in Computation Science and mendion in Machine Learning. Manages Python and Java expertise, TypeScript, SQL, Docker-based environments, technical documentation and LLM-assisted development. Connect software architecture, internal developer tooling, ML pipeline reliability and production inference systems.}%
}\\
\end{tabularx}

\vspace{1.2em}
\lettersection{Cover letter}

Dear Assaia team,

I am applying for the Software Engineer role because it fits the direction in which I am developing my engineering profile: software around ML systems, pipeline tooling, inference infrastructure, and internal platforms that make model work usable in production.

My background combines Software Engineering studies with ML/AI specialization, backend foundations, REST APIs, SQL, Linux, Git, technical documentation, and repository-based project work. I also bring a previous background in regulated banking and insurance operations, where reliability, traceability, process discipline, data quality, and failure handling were part of daily work.

What interests me most about this role is the bridge between ML research and production software. I am not applying from a pure research profile, but from a software engineering perspective: understanding existing systems, turning technical needs into maintainable tooling, documenting decisions, and building reliable paths between experimental work and operational use.

I use LLM tools as part of my engineering workflow, but with review, structure, and technical judgement rather than as a substitute for understanding the code. That is also how I approach AI systems more broadly: models are valuable components, but production value comes from the surrounding software, data flow, tooling, tests, monitoring, and operational constraints.

I would welcome the opportunity to discuss how my software engineering background, ML/AI direction, and operational discipline could contribute to Assaia's ML Core team.

\vspace{0.8em}
Best regards,\par
\vspace{0.35em}
{\bfseries Dídac Llorens}

\vfill
{\color{line}\hrule}
\vspace{0.45em}
{\scriptsize\color{muted}\ttfamily This letter is intended as a focused application note for Assaia's Software Engineer role. Project and profile links are included in the header for quick verification.}

\end{document}
