\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[a4paper,margin=1.7cm]{geometry}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage[
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue
]{hyperref}

\definecolor{accentblue}{HTML}{2563EB}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.35em}
\setlist[itemize]{leftmargin=1.2em,itemsep=0.2em,topsep=0.2em}
\newcommand{\cvsection}[1]{\vspace{0.6em}{\large\bfseries\color{accentblue}#1}\par\vspace{0.15em}\hrule\vspace{0.45em}}

\begin{document}

{\LARGE\bfseries Dídac Llorens}\quad
\href{mailto:didacllorensbravo@hotmail.com/}{didacllorensbravo@hotmail.com}\\
Software Engineering · ML/AI · Agentic Systems · Barcelona\\
\href{https://didacll.github.io/AgenticCareerBoost/}{didacll.github.io/AgenticCareerBoost}
\quad
\href{https://github.com/DidacLL}{github.com/DidacLL}
\quad
\href{https://www.linkedin.com/in/didacllorens/}{linkedin.com/in/didacllorens}


\cvsection{Profile}

Software Engineering student at Universitat Oberta de Catalunya, specializing
in Machine Learning and Artificial Intelligence and graduating in February
2027. Building public, inspectable engineering artifacts around agentic systems,
LaTeX tooling, and data/ML-oriented software. Fifteen years of banking and
insurance operations before engineering: regulated processes, high-volume case
resolution, team leadership, and stakeholder communication under pressure.

\cvsection{Target Roles}

ML engineering, data engineering, agentic AI, platform/tooling, research
engineering, regulated-domain software, and documentation-heavy engineering
roles where systems thinking and investigation matter.

\cvsection{Selected Projects}

\begin{tabularx}{\linewidth}{p{3.6cm} X}
\textbf{AgenticCareerBoost} &
Path-based, model-agnostic multi-agent operating system for engineering career
development. Uses 6 agent roles, 7 workflow contracts, formal truth hierarchy,
LaTeX reports, GitHub Pages, and public evidence trails.\\
\textbf{P3CTeX} &
Custom LaTeX document class and package ecosystem for academic document
production. Demonstrates tooling depth, package architecture, documentation,
and open-source discipline.\\
\textbf{p3cTeX-UMLST} &
Standalone UML diagram and code listing packages extracted from P3CTeX. Shows
modularization and package extraction from a larger LaTeX system.\\
\textbf{IronBank} &
Java/Spring Boot microservices banking simulation from IronHack. Older capstone
project, useful as backend evidence after README cleanup.\\
\end{tabularx}

\cvsection{Technical Stack}

\textbf{Languages:} Python, Java, Kotlin, SQL, LaTeX, JavaScript, Bash\\
\textbf{Frameworks/tools:} Spring Boot, Git, GitHub Actions, Maven, latexmk,
Linux, REST APIs\\
\textbf{Domains:} Machine Learning, Artificial Intelligence, agentic systems,
systems design, microservices, technical documentation, regulated-domain
software

\cvsection{Education}

\begin{tabularx}{\linewidth}{p{4.1cm} X}
\textbf{Universitat Oberta de Catalunya} &
Software Engineering, Machine Learning and Artificial Intelligence
specialization. Expected graduation: February 2027.\\
\textbf{IronHack} &
Java Backend Development bootcamp. Capstone: IronBank microservices banking
simulation.\\
\textbf{Additional training} &
Android/Kotlin app development at Fundación Francisco Puerto, FullStack React at Barcelona ITAcademy and
Linux administration at PUE-Consorci per a la Formació Continua de Catalunya.\\
\end{tabularx}

\cvsection{Operations Background}

\begin{itemize}
  \item 15 years in customer-facing banking and insurance operations.
  \item Team leadership, case triage, regulated processes, stakeholder
  communication, and high-volume problem resolution.
  \item Engineering relevance: data quality, compliance awareness, failure-mode
  thinking, audit trails, and systems that survive operational pressure.
\end{itemize}

\cvsection{Public Evidence}

\begin{itemize}
  \item Recruiter page:
  \href{https://didacll.github.io/AgenticCareerBoost/}{didacll.github.io/AgenticCareerBoost}
  \item AgenticCareerBoost:
  \href{https://github.com/DidacLL/AgenticCareerBoost}{github.com/DidacLL/AgenticCareerBoost}
  \item P3CTeX:
  \href{https://github.com/DidacLL/P3CTeX}{github.com/DidacLL/P3CTeX}
\end{itemize}

\end{document}
